### 2017-03-29 paper/oopsla17-submission/related.tex
related

In this section we describe three relevant aspects of related work:
%
programming languages approaches to diagnosing type errors,
%
software engineering approaches to fault localization, and
%
applying machine learning techniques to problems in programming languages.

@@

\subsection{Fault Localization}
Given a defect, fault localization is the task of identifying
``suspicious'' program elements (e.g., lines, statements) that are likely
implicated in the defect (i.e., that should be changed to fix the defect).
Perhaps the best-known is Tarantula, which uses a simple mathematical
formula based on measured information from dynamic normal and buggy
runs~\citep{Jones2002-us}. Other similar approaches, including those of
\citet{Chen2002-qz} and \citet{Abreu2006-fn,Abreu2007-mu} consider alternate features
of information or refined formulae and generally obtain more precise
results; see \citet{Wong2009-pd} for a survey. While some researchers have
approached such fault localization with an eye toward optimality (e.g.,
\citet{Yoo2013-rw} determine optimal coefficients), in general
such fault localization approaches are limited by their reliance on either
running tests or including relevant features. For example, Tarantula-based
techniques require a normal and a buggy run of the program. By contrast,
we consider incomplete programs with type errors that may not be executed
in any standard sense. Similarly, the features available influence the
classes of defects that can be localized. A fault localization scheme based
purely on control flow features lines will have difficulty with cross-site
scripting or SQL code injection attacks, which follow the same control flow
path on normal and buggy runs (differing only in the user-supplied data).
By contrast, we \ES{TODO}.

\subsection{Machine Learning for Programming Languages}
\label{sec:ml-pl}

>>>>

In this section we describe two relevant aspects of related work:
%
programming languages approaches to diagnosing type errors, and
%
software engineering approaches to fault localization.
%
% applying machine learning techniques to problems in programming languages.

@@

\subsection{Fault Localization}
Given a defect, \emph{fault localization} is the task of identifying
``suspicious'' program elements (\eg lines, statements) that are likely
implicated in the defect (\ie that should be changed to fix the defect)
%
--- thus, type error localization can be viewed as an instance of fault
localization.
%
The best-known fault localization technique is likely Tarantula, which
uses a simple mathematical formula based on measured information from
dynamic normal and buggy runs~\citep{Jones2002-us}.
%
Other similar approaches, including those of \citet{Chen2002-qz} and
\citet{Abreu2006-fn,Abreu2007-mu} consider alternate features of
information or refined formulae and generally obtain more precise
results; see \citet{Wong2009-pd} for a survey.
%
While some researchers have approached such fault localization with an
eye toward optimality (\eg \citet{Yoo2013-rw} determine optimal
coefficients), in general such fault localization approaches are limited
by their reliance on either running tests or including relevant
features.
%
For example, Tarantula-based techniques require a normal and a buggy run
of the program.
%
By contrast, we consider incomplete programs with type errors that may
not be executed in any standard sense.
%
Similarly, the features available influence the classes of defects that
can be localized.
%
A fault localization scheme based purely on control flow features
will have difficulty with cross-site scripting or SQL code injection
attacks, which follow the same control flow path on normal and buggy
runs (differing only in the user-supplied data).
%
Our feature set is comprised entirely of syntactic and typing features,
a natural choice for modeling type errors, but it would likely not
generalize to other types of defects.

% \subsection{Machine Learning for Programming Languages}
% \label{sec:ml-pl}
